Active learning stopping criteria

### 2020-09-24 analysis/hyper_criteriaR.Rmd
add missing function within functgion
rmd

---
title: "Active learning stopping criteria"
output: html_notebook
---

@@

>>>>

---
title: "Active learning stopping criteria"
output: html_document
---

@@

  # what's the minimum number of relevant documents there would have to be in the 
  # unseen documents + the sample in order for our target to be missed
  get_khat <- function(r_ML, r_seen, recall_target){
    return(floor(r_seen/recall_target-r_ML+1))
  }
